Explorations to Optimize the Parareal Algorithm \\to Solve ODEs in Given Applications

### 2014-12-10 paper.tex
Merge remote-tracking branch 'origin/master'
Conflicts:
	paper.tex

\begin{figure}
\begin{center}
\includegraphics[width=0.75\textwidth]{data/runtime_vs_cpus.pdf}
\caption{Running time vs. number of CPUs.}
\label{fig:run_v_cpu}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=0.75\linewidth]{data/error_vs_corrections.pdf}
\caption{Error vs. number of correction steps.}
\label{fig:err_v_k}
\end{center}
\end{figure}

@@

\begin{center}
\begin{tabular}{|c|c|c|c|c|} \hline
($N_x, N_y$) & $P_x$ & $P_y$ & Time (sec) \\ \hline
(128, 128) & 2 & 2 & (still queued on Odyssey)\\ \hline
(128, 128) & 4 & 2 & 2.31 \\ \hline %check
(128, 128) & 4 & 4 & (still queued on Odyssey) \\ \hline
(128, 128) & 8 & 8 & (still queued on Odyssey) \\ \hline
(256, 256) & 2 & 2 & 2.57 \\ \hline %real
(256, 256) & 4 & 2 & 11.32 \\ \hline %check
(256, 256) & 4 & 4 & 13.65 \\ \hline %check
(256, 256) & 8 & 8 & 17.44 \\ \hline %check
(512, 512) & 2 & 2 & (still queued on Odyssey)\\ \hline
(512, 512) & 4 & 2 & (still queued on Odyssey)\\ \hline
(512, 512) & 4 & 4 & (still queued on Odyssey)\\ \hline %check
(512, 512) & 8 & 8 & (still queued on Odyssey) \\ \hline %check
\end{tabular}
\end{center}

>>>>

\begin{figure}
\begin{center}
\includegraphics[width=0.75\textwidth]{data/runtime_vs_cpus.pdf}
\caption{Running time vs. number of CPUs.}
\label{fig:run_v_cpu}
\end{center}
\end{figure}
`
\begin{figure}
\begin{center}
\includegraphics[width=0.75\linewidth]{data/error_vs_corrections.pdf}
\caption{Error vs. number of correction steps.}
\label{fig:err_v_k}
\end{center}
\end{figure}

@@

\begin{center}
\begin{tabular}{|c|c|c|c|c|} \hline
($N_x, N_y$) & $P_x$ & $P_y$ & Time (sec) \\ \hline
(128, 128) & 2 & 2 & (still queued on Odyssey)\\ \hline
(128, 128) & 4 & 2 & 2.31 \\ \hline
(128, 128) & 4 & 4 & (still queued on Odyssey) \\ \hline
(128, 128) & 8 & 8 & (still queued on Odyssey) \\ \hline
(256, 256) & 2 & 2 & 2.57 \\ \hline %real
(256, 256) & 4 & 2 & 11.32 \\ \hline
(256, 256) & 4 & 4 & 13.65 \\ \hline
(256, 256) & 8 & 8 & 17.44 \\ \hline
(512, 512) & 2 & 2 & (still queued on Odyssey)\\ \hline
(512, 512) & 4 & 2 & (still queued on Odyssey)\\ \hline
(512, 512) & 4 & 4 & (still queued on Odyssey)\\ \hline %check
(512, 512) & 8 & 8 & (still queued on Odyssey) \\ \hline %check
\end{tabular}
\end{center}
